ODGI: understanding pangenome graphs

### 2021-11-10 manuscript/fig_extract_viz_draw_position_untangle.tex
be consistent with the `odgi untangle` output. C4A is before C4B in the reference

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4B} gene is missing. \vspace{-1em}

>>>>

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4A} gene is missing. \vspace{-1em}
